### 2019-03-08 experiments.tex
improve threats

There are several primary threats to validity:  first, our empirical
results are limited to a small set of Python programs, ranging from
relatively small and simple to large and complex libraries; the
representative nature of these subjects is not clear.
Furthermore, because
no other tools implement the kind of approach taken here, based on
automated generation of value pool based unit tests for a system
(imperative property-based testing), to our knowledge, we were unable
to perform a meaningful comparison with another nondeterminism
detection tool.  Available tools, such as DeFlaker
(\url{http://www.deflaker.org/}), perform a completely different task (DeFlaker
is essentially a plugin for Maven regression tests, and cannot check
nondeterminism at any smaller granularity than that of a whole tests's
pass/fail result) and target the Java language.  However, the primary
aim of our results is to show 1) that nondeterminism at the library
level can exist in real Python programs, 2) that it can be detected
by an implementation of the formalism proposed in this paper, and 3)
that the overhead for such detection, and cost to delta-debug
nondeterministic tests, is not prohibitive.  We believe that the case
studies show that users testing Python libraries, and concerned about
nondeterminism, would find the TSTL tools useful, and would be able to
detect and debug nondeterministic behavior using our approach, a
functionality that we believe to be unique in the automated test generation
literature (and supported in no other tool).

>>>>

There are several primary threats to validity:  first, our empirical
results are limited to a small set of Python programs, ranging from
relatively small and simple to large and complex libraries; the
representative nature of these subjects is not clear.
Furthermore, because
no other tools implement the kind of approach taken here, based on
automated generation of value pool based unit tests for a system
(imperative property-based testing), to our knowledge, we were unable
to perform a meaningful comparison with another nondeterminism
detection tool.  Available tools, such as DeFlaker \cite{bell2018d}
(\url{http://www.deflaker.org/}), perform a completely different task (DeFlaker
is essentially a plugin for Maven regression tests, and cannot check
nondeterminism at any smaller granularity than that of a whole tests's
pass/fail result) and target the Java language.  iDFlakies
\cite{idflakies}, similarly, ``does not further classify the causes of
the flaky tests'' beyond identifying them as likely related to test
order, or not.

However, the primary
aim of our results is to show 1) that nondeterminism at the library
level can exist in real Python programs, 2) that it can be detected
by an implementation of the formalism proposed in this paper, and 3)
that the overhead for such detection, and cost to delta-debug
nondeterministic tests, is not prohibitive.  We believe that the case
studies show that users testing Python libraries, and concerned about
nondeterminism, would find the TSTL tools useful, and would be able to
detect and debug nondeterministic behavior using our approach, a
functionality that we believe to be unique in the automated test generation
literature (and supported in no other tool).  Comparison with a
competing tool is not required to validate the basic idea, since
precise empirical measurements of overheads, or improvements on an
existing approach, are not proposed for evaluation.
